---
title: "PiB"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(ggplot2)
library(ggfortify)
library(Rtsne)
library(reshape2)
theme_set(theme_minimal())
```

# CONTRACT REGION OF INTERESTED EXPORTS

## Page 1 contract exports

```{r}

p1_initials_II <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 1 contract exports/190910,21h19_II initials page 1.txt", sep = "")

p1_initials_III <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 1 contract exports/190910,21h19_III initials page 1.txt", sep = "")

p1_initials_SF <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 1 contract exports/190910,21h19_SF initials page 1.txt", sep = "")


colnames(p1_initials_SF) <- c("spectrum", "P1_SF_intensity")
colnames(p1_initials_II) <- c("spectrum", "P1_II_Intensity")
colnames(p1_initials_III) <- c("spectrum", "P1_III_Intensity")
```

## Page 2 contract exports

```{r}

p2_initials_II <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 2 contract exports/190910,23h44_II initials page 2.txt", sep = "")

p2_initials_III <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 2 contract exports/190910,23h44_III initials page 2.txt", sep = "")

p2_initials_SF <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 2 contract exports/190910,23h44_SF initials page 2.txt", sep = "")

colnames(p2_initials_SF) <- c("spectrum", "P2 SF Intensity")
colnames(p2_initials_II) <- c("spectrum", "P2 II Intensity")
colnames(p2_initials_III) <- c("spectrum", "P2 III Intensity")

```

## Page 3 contract export

```{r}

p3_initials_II <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 3 contract export/190910,01h50_II initials signature page 3.txt", sep = "")

p3_initials_III <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 3 contract export/190910,01h50_III initials signature page 3.txt", sep = "")

p3_initials_SF <- read.table(file = "CONTRACT REGION OF INTERESTED EXPORTS/Page 3 contract export/190910,01h50_SFsignature page 3.txt", sep = "")

colnames(p3_initials_SF) <- c("spectrum", "P3 SF Intensity")
colnames(p3_initials_II) <- c("spectrum", "P3 II Intensity")
colnames(p3_initials_III) <- c("spectrum", "P3 III Intensity")

```

# INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS

## full squares

```{r}

sq1_under_no1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/full squares/Full square 1 underneat number 1.txt", sep = "")

sq1_under_no2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/full squares/Full square 1 underneat number 2.txt", sep = "")

sq2_under_no1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/full squares/Full square 2 underneat number 1.txt", sep = "")

sq_beside_no4 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/full squares/Full square beside number 4.txt", sep = "")

sq1_under_no3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/full squares/Full square underneat number 3.txt", sep = "")

sq2_under_no2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/full squares/II full square ink under number 2.txt", sep = "")

sq2_under_no3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/full squares/II full square ink under number 3.txt", sep = "")

colnames(sq1_under_no1) <- c("spectrum", "SQ1 U1 Intensity")
colnames(sq1_under_no2) <- c("spectrum", "SQ1 U2 Intensity")
colnames(sq2_under_no1) <- c("spectrum", "SQ2 U1 Intensity")
colnames(sq_beside_no4) <- c("spectrum", "SQ B4 Intensity")
colnames(sq1_under_no3) <- c("spectrum", "SQ1 U3 Intensity")
colnames(sq2_under_no2) <- c("spectrum", "SQ2 U2 Intensity")
colnames(sq2_under_no3) <- c("spectrum", "SQ2 U3 Intensity")

```

## numbers

```{r}

sq_no2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/numbers/squares analysis_number 2.txt", sep = "")

sq_no3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/numbers/squares analysis_number 3.txt", sep = "")

sq_no4 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/numbers/squares analysis_number 4.txt", sep = "")

sq_no1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/numbers/squares analysis_number1.txt", sep = "")

sq_no2_II <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/numbers/squares_analysis_number 2.txt", sep = "")

sq_no5 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/numbers/squares_analysis_number 5.txt", sep = "")

sq_no6 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/numbers/squares_analysis_number 6.txt", sep = "")

colnames(sq_no2) <- c("spectrum", "SQ 2 Intensity")
colnames(sq_no3) <- c("spectrum", "SQ 3 Intensity")
colnames(sq_no4) <- c("spectrum", "SQ 4 Intensity")
colnames(sq_no1) <- c("spectrum", "SQ 1 Intensity")
colnames(sq_no2_II) <- c("spectrum", "SQ2 2 Intensity")  # I think this df should be sq2 from number 1
colnames(sq_no5) <- c("spectrum", "SQ 5 Intensity")
colnames(sq_no6) <- c("spectrum", "SQ 6 Intensity")

```

## split squares_each square 3 ROI

```{r}

# square II under no1
sqII_no1_ROI1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/II square ink under number 1_ROI1.txt", sep = "")
sqII_no1_ROI2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/II square ink under number 1_ROI2.txt", sep = "")
sqII_no1_ROI3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/II square ink under number 1_ROI3.txt", sep = "")

colnames(sqII_no1_ROI1) <- c("spectrum", "SQ2 1 ROI1 Intensity")
colnames(sqII_no1_ROI2) <- c("spectrum", "SQ2 1 ROI2 Intensity")
colnames(sqII_no1_ROI3) <- c("spectrum", "SQ2 1 ROI3 Intensity")

# square above no5
sq_no5_ROI1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink above number 5_ROI1.txt", sep = "")
sq_no5_ROI2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink above number 5_ROI2.txt", sep = "")
sq_no5_ROI3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink above number 5_ROI3.txt", sep = "")

colnames(sq_no5_ROI1) <- c("spectrum", "SQ 5 ROI1 Intensity")
colnames(sq_no5_ROI2) <- c("spectrum", "SQ 5 ROI2 Intensity")
colnames(sq_no5_ROI3) <- c("spectrum", "SQ 5 ROI3 Intensity")

# square above no6
sq_no6_ROI1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink above number 6_ROI1.txt", sep = "")
sq_no6_ROI2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink above number 6_ROI2.txt", sep = "")
sq_no6_ROI3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink above number 6_ROI3.txt", sep = "")

colnames(sq_no6_ROI1) <- c("spectrum", "SQ 6 ROI1 Intensity")
colnames(sq_no6_ROI2) <- c("spectrum", "SQ 6 ROI2 Intensity")
colnames(sq_no6_ROI3) <- c("spectrum", "SQ 6 ROI3 Intensity")

# square beside no4
sq_no4_ROI1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink beside number 4_ROI1.txt", sep = "")
sq_no4_ROI2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink beside number 4_ROI2.txt", sep = "")
sq_no4_ROI3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink beside number 4_ROI3.txt", sep = "")

colnames(sq_no4_ROI1) <- c("spectrum", "SQ 4 ROI1 Intensity")
colnames(sq_no4_ROI2) <- c("spectrum", "SQ 4 ROI2 Intensity")
colnames(sq_no4_ROI3) <- c("spectrum", "SQ 4 ROI3 Intensity")

# square I under no1
sqI_no1_ROI1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 1_ROI1.txt", sep = "")
sqI_no1_ROI2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 1_ROI2.txt", sep = "")
sqI_no1_ROI3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 1_ROI3.txt", sep = "")

colnames(sqI_no1_ROI1) <- c("spectrum", "SQI 1 ROI1 Intensity")
colnames(sqI_no1_ROI2) <- c("spectrum", "SQI 1 ROI2 Intensity")
colnames(sqI_no1_ROI3) <- c("spectrum", "SQI 1 ROI3 Intensity")

# square under no2
sq_no2_ROI1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 2_ROI1.txt", sep = "")
sq_no2_ROI2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 2_ROI2.txt", sep = "")
sq_no2_ROI3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 2_ROI3.txt", sep = "")

colnames(sq_no2_ROI1) <- c("spectrum", "SQ 2 ROI1 Intensity")
colnames(sq_no2_ROI2) <- c("spectrum", "SQ 2 ROI2 Intensity")
colnames(sq_no2_ROI3) <- c("spectrum", "SQ 2 ROI3 Intensity")

# square under no3
sq_no3_ROI1 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 3_ROI1.txt", sep = "")
sq_no3_ROI2 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 3_ROI2.txt", sep = "")
sq_no3_ROI3 <- read.table(file = "INK SQUARE ANALYSIS (TRAINING SET)-roi EXPORTS/split squares_each square 3 ROI/square ink under number 3_ROI3.txt", sep = "")

colnames(sq_no3_ROI1) <- c("spectrum", "SQ 3 ROI1 Intensity")
colnames(sq_no3_ROI2) <- c("spectrum", "SQ 3 ROI2 Intensity")
colnames(sq_no3_ROI3) <- c("spectrum", "SQ 3 ROI3 Intensity")

```

# STRIKES ANALYSIS (I TEST SET)-ROI EXPORTS

```{r}

strike1 <- read.table(file = "STRIKES ANALYSIS (I TEST SET)-ROI EXPORTS/strike 1.txt", sep = "")

strike2 <- read.table(file = "STRIKES ANALYSIS (I TEST SET)-ROI EXPORTS/strike 2.txt", sep = "")

strike3 <- read.table(file = "STRIKES ANALYSIS (I TEST SET)-ROI EXPORTS/strike 3.txt", sep = "")

strike4 <- read.table(file = "STRIKES ANALYSIS (I TEST SET)-ROI EXPORTS/strike 4.txt", sep = "")

strike5 <- read.table(file = "STRIKES ANALYSIS (I TEST SET)-ROI EXPORTS/strike 5.txt", sep = "")

strike6 <- read.table(file = "STRIKES ANALYSIS (I TEST SET)-ROI EXPORTS/strike 6.txt", sep = "")

colnames(strike1) <- c("spectrum", "strike1 Intensity")
colnames(strike2) <- c("spectrum", "strike2 Intensity")
colnames(strike3) <- c("spectrum", "strike3 Intensity")
colnames(strike4) <- c("spectrum", "strike4 Intensity")
colnames(strike5) <- c("spectrum", "strike5 Intensity")
colnames(strike6) <- c("spectrum", "strike6 Intensity")

```

```{r}

test_data <- cbind(strike1, strike2[2], strike3[2], strike4[2], strike5[2], strike6[2])
training_data1 <- cbind(sq1_under_no1, sq2_under_no1[2], sq1_under_no2[2], sq2_under_no2[2], sq1_under_no3[2], sq2_under_no3[2])
training_data2 <- cbind(sq_no1, sq_no2[2], sq_no2_II[2], sq_no3[2], sq_no4[2], sq_no5[2], sq_no6[2])
training_data3 <- cbind(sqI_no1_ROI1, sqI_no1_ROI2[2], sqI_no1_ROI3[2], sqII_no1_ROI1[2], sqII_no1_ROI2[2], sqII_no1_ROI3[2], sq_no2_ROI1[2], sq_no2_ROI2[2], sq_no2_ROI3[2], sq_no3_ROI1[2], sq_no3_ROI2[2], sq_no3_ROI3[2], sq_no4_ROI1[2], sq_no4_ROI2[2], sq_no4_ROI3[2], sq_no5_ROI1[2], sq_no5_ROI2[2], sq_no5_ROI3[2], sq_no6_ROI1[2], sq_no6_ROI2[2], sq_no6_ROI3[2])

```

# PCAs
## Test_data
Changing the columns so they are rows:

```{r}
test<-as.data.frame(t(test_data[-1]))
names(test)<-test_data$spectrum

test$labels=row.names(test)
```

```{r}
#doing PCA
pca_res <- prcomp(test[0:4500], scale. = TRUE)
autoplot(pca_res,data=test,colour="labels", label=T)
```

## training_data1

Changing the columns so they are rows:

```{r}
test<-as.data.frame(t(training_data1[-1]))
names(test)<-training_data1$spectrum

test$labels=row.names(test)
```

```{r}
#doing PCA
pca_res <- prcomp(test[0:4500], scale. = TRUE)
autoplot(pca_res,data=test,colour="labels", label=T)
```

## training_data2

Changing the columns so they are rows:

```{r}
test<-as.data.frame(t(training_data2[-1]))
names(test)<-training_data2$spectrum

test$labels=row.names(test)
```

```{r}
#doing PCA
pca_res <- prcomp(test[0:4500], scale. = TRUE)
autoplot(pca_res,data=test,colour="labels", label=T)
```

## training_data3

Changing the columns so they are rows:

```{r}
test<-as.data.frame(t(training_data3[-1]))
names(test)<-training_data3$spectrum

test$labels=row.names(test)
```

```{r}
#doing PCA
pca_res <- prcomp(test[0:4500], scale. = TRUE)
autoplot(pca_res,data=test,colour="labels", label=T)
```
